Embedded Scalars: {A}n Experimental Revisit

### 2014-05-28 text/paper/paper4.tex
integrated the Bayesian analysis

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[node distance = 2.5cm, 
    double distance = 2pt,
    minimum size=1.25cm,
    thick]

@@

    \node[left of = anchor, node distance= 0.5cm] (k) {$k \in
      \set{\text{as-n, as-e, \dots}}$};

@@

    \draw[->] (q)--(t);

    \draw[->] (p)--(t);

    \draw[->] (e)--(t);

@@

    \begin{scope}[xshift = 7.5cm, node distance = 1cm]

@@

      \node[above of = td] (pd) {$\myvec{p}_k =
        \text{Dirichlet}(\tuple{\nicefrac{1}{k}, \nicefrac{1}{k}, \dots})$};

@@

  \end{tikzpicture}
  \caption{Probabilistic graphical model}
  \label{fig:model_graph}
\end{figure}

>>>>

\begin{figure}[]
  \centering
  \begin{tikzpicture}[node distance = 2.5cm, 
    double distance = 2pt,
    minimum size=1.25cm,
    thick]

@@

    \node[left of = anchor, node distance= 0.95cm] (k) {$k \in
      \set{\text{\as-ntr, \as-acc, \dots}}$};

@@

    \draw[->,shorten >=0.05cm] (q)--(t);

    \draw[->,shorten >=0.05cm] (p)--(t);

    \draw[->,shorten >=0.05cm] (e)--(t);

@@

    \begin{scope}[xshift = 6.5cm, node distance = 1cm]

@@

      \node[above of = td] (pd) {$\myvec{p}_k \sim
        \text{unbiased Dirichlet}$};

@@

  \end{tikzpicture}
  \caption{Probabilistic graphical model. All nodes represent
    variables, arrows represent functional relations between them.
    Using conventions of \citet{LeeWagenmakers2013:Bayesian-Cognit},
    the higher a node, the more latent it is. Square nodes represent
    discrete-valued variables, circular squares represent
    continuous-valued variables. Gray squares show the observable
    variables. Double-lined nodes show deterministic dependency on
    values of input nodes. The variables in the box are repeated for
    each of the $k$ relevant conditions.}
  \label{fig:model_graph}
\end{figure}

\paragraph{Model fitting.} We use JAGS
\citep{Plummer2003:JAGS:-A-Program} to estimate the posteriors over
paramater values given our data. Results reported here are based on
two chains of 10.000 samples from the joint posterior distribution
MCMC sampling, obtained after an initial burn-in of 10.000 steps. The
latter guaranteed convergence.

, we obtain estimates
for the posterior of the latent parameters given the data. To check
whether the model yields sensible results we first look at the
preference-related control conditions.
%
\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{pics/post_salience_TF.pdf}
  \caption{Estimated posteriors for the relative salience of \lc- and
    \ec-readings for different intonational cues. The lines under the
    curves mark the estimated 95\% HDIs (see Footnote~\ref{fn:HDI}).}
  \label{fig:Posterior_TF}
\end{figure}
%
Estimates for the posteriors over relative salience levels for
target-related controls are plotted in
Figure~\ref{fig:Posterior_TF}. The results are exactly as we would
expect them to be. Given our data, we should believe that the
\lc-reading is most prominent. But the level of prominence varies with
accentuation. Under prosody that we hypothesized would favor the
\lc-reading, the contrast is most pronounced. Contrarily, accentuation
that we hypothesized favors the \ec-reading we are no longer justified
in believing that the late-closure reading is certainly preferred
(witness the clearly overlapping 95\% HDIs).\footnote{\label{fn:HDI} A
  95\% Highest Density Interval (HDI) is a convex region of values
  over which 95\% of the distribution's probability density is
  divided, such that no value outside of that region has higher
  probability density than any point within
  \citep{Kruschke2011:Doing-Bayesian-}. Intuitively speaking, the 95\%
  HDI is the set of values which we may believe to be true with some
  confidence; what falls outside this region is what can be excluded
  with relative safety.}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{pics/post_salience.pdf}
  \caption{Posteriors over relative salience of target readings in
    critical conditions.}
  \label{fig:Posterior_T}
\end{figure}

Estimates of posteriors over salience of readings in the target
conditions are given in Figure~\ref{fig:Posterior_T}. In the
\es-conditions, literal readings are by far the most salient, followed
by local, followed by global readings. There does not appear to be a
significant effect of intonation (by visual comparison of 95\%
HDIs). For \as-sentences, the same preference order holds in tendency,
but we cannot assert with full confidence that local readings are
attested or that they are preferred over global readings (see below).

Posteriors over error rates are conceptually less interesting, and we
will skip them here. Posteriors over the sequential bias parameter are
shown in Figure~\ref{fig:post_q}, and show that, given the model and
our data, we have reason for believing in a bias for late responses.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{pics/post_q.pdf}
  \caption{Estimated Posteriors over global sequential bias parameter
    $q$.}
  \label{fig:post_q}
\end{figure}

\paragraph{Model validation.} As a crude sanity check that our model
is able to predict the observed data, we gathered 10.000 random values
from the posterior predictive distribution and found a highly
significant correlation between these and the observed data ($R^2 =
0.987$, $p < 0.001$).

\paragraph{Hypothesis testing.} We are chiefly interested in two
questions: (i) which readings are available? and (ii) what is the
preference order over readings?

The first question can be answered by looking at the HDIs of the
posteriors of the candidate readings. The HDIs give the region of the
95\% least unbelievable parameter values, given the data and the
model. We would like to check the hypothesis that a given reading is
unavailable, i.e., its activation value in the probabilistic model is
equal to 0, or close to zero for practical purposes (Region of
Practical Equivalence, ROPE). We reject the ``null-hypothesis'' that
the true value is 0 if its ROPE lies entirely outside the 95\% HDI; we
accept the ``null-hypothesis'' if the ROPE lies entirely within the
95\% HDI \citep[][Ch.~12]{Kruschke2011:Doing-Bayesian-}. The following
table lists approximations of the 95\% HDIs for each condition and
reading:

\begin{center}
  \begin{tabular}{lllllll}
    & lit & loc & glb & \\ \midrule
    \as-ntr & $(0.924 , 1)$ & $(0 , 0.068)$
    & $(0 , 0.022)$ \\
    \as-acc 
    & $(0.816 , 0.964)$
    & $(0.028 , 0.152)$
    & $(0 , 0.066)$ \\
    \es-ntr 
    & $(0.665 , 0.873)$
    & $(0.117 , 0.323)$
    & $(0 , 0.024)$ \\
    \es-acc 
    & $(0.634 , 0.851)$
    & $(0.139 , 0.356)$
    & $(0 , 0.022)$ 
  \end{tabular}
\end{center}

\noindent We should thus accept the hypothesis that there are no
global readings at all, and no local readings for \as-sentence under
neutral intonation. There is support for a belief in local readings in
the \as-acc condition up to a ROPE of $[0;0.028)$.

The question after the preference relations between readings can be
answered in a similar way. Here, we look at the posterior beliefs
about the differences of activation strengths and ask whether these
posterior beliefs allow us to safely conclude that differences are
bigger than zero or not. It is obvious enough that literal readings
are always the most preferred, and that local readings are preferred
over global readings for \es-sentences. Figure~\ref{fig:PostDiffTAS}
shows the posteriors over differences between local and global
readings for \as-sentences. Since the 95\% HDIs include 0, the data
provides no ground for confidence that, given the model, local
readings of \as-sentences are preferred over global ones, despite the
obvious tendency. In sum, with the exception of remaining uncertainty
about local readings of \as-sentences, the model and the data suggest
that global readings are absent entirely, while literal readings are
preferred over local readings.

\begin{figure}
  \centering
  \subfloat[neutral][]{
      \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
  }
  \hfill
  \subfloat[accented][]{
      \includegraphics[width=0.45\textwidth]{PostDiffT_ASntr.pdf}
  }
  \caption{Posteriors over differences between salience levels for
    local and global readings of \as-sentences.}
  \label{fig:PostDiffTAS}
\end{figure}
